Material Metohds

### 2019-09-16 doc/MatMeth.Rmd
made Intro md file and other writing updates
editing to material and methods

## Mouse Husbandry

1.	(Specific strains were obtained from X vendors, 2.
2.	3 separate rooms used (precautions taken to ensure there was limited environmental variance) b. X additional husbandry things done to help with breeding of some mouse strains. housed in X conditions (extra things done for problem breeders,
3.	euthanized under X protocol,
4. mention results if there was a detectable environmental effect

The Wild derived inbred strains PWD/PhJ, PERC/Eij, WSB/EiJ, LEWE/EiJ, MSM/MsJ, MOLF/EiJ, CAST/EiJ, CZECHII/EiJ, CORLI/EiJ and SPRET/EiJ were purchased from Jax labs (Maine USA). 
The strains of KAZ/TUA, TOM/TUA, AST/TUA, HMI/TUA and SPIC) were ordered and cryo-derived from BRC at RIKEN (Japan) website). All mice were housed UW-Madison Biotech and MSC facilities - following the protocols.
 A breeding colony of wild derived mice sampled from Gough Island were housed at UW Veterinary school facilities.  (some of the other strains housed there - comparisons were made of strains housed across different facilities to (test if there was an effect of mouse room of MLH1 counts).

Mice were feed on dry standard breeder chow. Some strains sunflower seeds, nestlets and larger cages were added to improve fertility and litter survival. Adult mice were euthanized by CO asphyxiation. Neonate and embryonic mice were euthanized by decapitation following the protocols approved by the Institutional Animal Care and Use Committee at the University of Wisconsin-Madison.

## Tissue Collection and Immunohistochemistry

1.	describe how gonad tissue was collected)  (right testes, both ovaries) (tunica removed decapsulated)  X protocol for testes,   X protocol for ovaries.  X ages for males, X ages for females
2.	 describe spread process   (describe process - clearly point out the distinctions for testes and ovaries
3.	(describe staining process (with DMC1)  (same process)

@@

Meiocyte spreads were made following  [@peters_1997] Peters et al 2001. For testes the tunica was removed and whole testes was incubated in 3ml of hypotonic solution for 45min. For ovaries after dissection, the pair of ovaries were decapsulated in cold PBS and both were incubated in 300ul of hypotonic solution for 45 min.

@@

## Image Processing

1.	Basic quality criteria,
2.	Manual quant pipeline for MLH1 (anonimized)
3.	Quanti pipeline for DMC1 (not completely finished)

@@

## Statisical Analysis

>>>>

```{r set.up, echo=FALSE}
#set wd
#load datafile
```

# Mouse Husbandry

To access natural genetic variation for *Mus musculus*, Wild derived inbred strains strains were used. PWD/PhJ, PERC/Eij, WSB/EiJ, LEWE/EiJ, MSM/MsJ, MOLF/EiJ, CAST/EiJ, CZECHII/EiJ, CORLI/EiJ and SPRET/EiJ were purchased from Jax labs (https://www.jax.org) (Maine USA). The strains of KAZ/TUA, TOM/TUA, AST/TUA, HMI/TUA and SPIC) were cryo-derived from Biological Resource Center (BRC) at RIKEN (Ibaraki, Japan) (https://en.brc.riken.jp/). All mice were housed UW-Madison Biotech and MSC facilities - following the protocols.  A breeding colony of wild derived mice sampled from Gough Island (GI )is maintained at UW Veterinary school facilities.
 Mice were feed on dry standard breeder chow. Some strains sunflower seeds, nestlets and larger cages were added to improve fertility and litter survival. Adult mice were euthanized by CO asphyxiation. Neonate and embryonic mice were euthanized by decapitation following the protocols approved by the Institutional Animal Care and Use Committee at the University of Wisconsin-Madison.

Over the coruse of data collection some breeding colonies / mice were moved from facilities. Additionally the GI strain was kept at a seperate facility.  (eviddence for environmental (room) effect on (MLH1 / SC lengths / a variety of meiotic traits was tested for. We observed no effect, Supplemental figure))

# Tissue Collection and Immunohistochemistry

@@

Meiocyte spreads were made following [@peters_1997]. For testes the tunica was removed and whole testes was incubated in 3ml of hypotonic solution for 45min. For ovaries after dissection, the pair of ovaries were decapsulated in cold PBS and both were incubated in 300ul of hypotonic solution for 45 min.

@@

# Image Processing

@@

# Statisical Analysis
